### 2021-12-17 manuscript.Rmd
added notes from today's meeting

@@

@@

>>>>

orcid_person("0000-0002-9689-4189")

@@

May need to manually edit some stuff
Figure out how to get information

Ideas from meeting:
- Career length: from first pub, from first degree
- Over time: are things becoming more varied
- Maybe we can use scholar if they don't have orcid
- Which journals are publishing this information
- Types of big team research (social, cognitive)
- Employment levels
- Education levels
- # Of works: separate to total, other/preprint, journal/book/traditional
- Limitations of this system

@@

But type here stuff and things
